Survival Analysis of Questions Posted on the iFixit Answers forum

### 2018-03-11 article/draft1.Rnw
added to Vitae section

Lisa Oshita is a senior undergraduate student at the California Polytechnic State University in San Luis Obispo, majoring in statistics...

>>>>

Lisa Oshita is a senior undergraduate statistics major at the California Polytechnic State University in San Luis Obispo. Shannon Pileggi is an Assistant Professor in the Statistics Department at California Polytechnic State University, San Luis Obispo. Anthony Pileggi is a Data Scientist at iFixit.
